Adaptability of ecophysiological traits define how plant lineages make a living in shaded environments 

### 2019-03-11 manuscript/manuscript.Rmd
pca plots drafted

---
title: "A Comparative Ecophysiological Survey of Lycophytes, Ferns, and Seed Plants"
author: 
date: 
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')
```

@@

# Stoichiometry (##can use pairwise for specific p values: see leaf P below)

@@

>>>>

---
title: "Adaptability of ecophysiological traits define how plant lineages make a living in shaded environments "
author: 
date: 
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---

\
Courtney E. Campany^1^, coauthors^1^ and Eddie Watkins Jr. ^1^

\
^1^ Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith, NSW, Australia

\
Corresponding author: C.E. Campany, email: courtneycampany@gmail.com, telephone: +1 607 279 7020

Running Head: Shade ecophysiology of plant lineages

```{r, results="asis", echo=FALSE, warning=FALSE}
library(knitr)
opts_knit$set(root.dir = '../')
```

```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
# Set Flag to include figures in text or not.
includeFigs <- FALSE
```

@@

## Stoichiometry (##can use pairwise for specific p values: see leaf P below)

@@

# Discussion

# Acknowledgements
We thank

# Tables {.unnumbered}
**Table 1**.

\
**Table 2**.

# Figures {.unnumbered}

```{r allometry, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/pca_plot.R")
```  
**Figure 1**. Redundancy analysis of measured functional traits across con-occuring angiosperms and fern species in open and shaded habitats. With the 12 measured variables, number% of the trait variation was accounted for in two dimensions. Variables include net photosynthesis (A~n~), stomatal conductance (g~s~), instantaneous water use efficiency (WUE), stomatal density (SD), the light compensation point (LCP), quantum yield ($$\phi$$), dark respiration (R~d~), foliar nitrogen (N) and phosphorus (P) content, the leaf carbon to nitrogen ratio (C:N) and the leaf nitrogen to phosphorus ratio (N:P).

```{r allometry, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/pca_canopy.R")
```  
**Figure 2**. Redundancy analysis of measured functional traits across con-occuring angiosperms fern and lycopyte species in shaded habitats.

# References {.unnumbered}
